---
title: "Ajoku-Asghar-Burton HW6"
author: "Oiza Ajoku, Anuba Asghar and Zachary Burton"
date: "10/21/2021"
output:
  word_document: default
---
---
title: "DSA-5103 Homework 6"
author:
  - Oiza Ajoku
  - Anuba Asghar
  - Zachary Burton
date: "10/21/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include=FALSE}
library(tidyverse)
library(readr)
library(dplyr)
library(knitr)
library(kableExtra)
library(forcats)
library(pandas)
library(Envstats)
library(outliers)
library(mice)
library(naniar)
library(pls)
library(lars)

test <- read.csv("Test.csv")
train <- read.csv("Train.csv")

attach(train)
```

## Question 1 (a) i. Data Understanding

#Our intial analysis began with a histogram of the revenue in the training dataset.
#   on intital oversvation there appears to be an outlier. We performed a grubs test
#   to verify. 


```{r echo = T, results = 'hide'}

hist(train$revenue)

outlierTest <- grubbs.test(train$revenue)
trainNoOutlier <- train[train$revenue != 15980.79,]

```

#From the results of the outlier, the p-value is < 0.05 and thus we can reject the
#   null hypothesis and verfiy that the record with the highest revenue (the revenue 
#   being 15980.79 in this case) is indeed an outlier and should be removed. 













